Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-08 paper.tex
Add TKE figure with subfigures

% Compare contours of TKE for 2 simulation cases and experiments

>>>>

% Compare contours of TKE for 2 simulation cases and experiments
\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering

        \includegraphics[width=0.95\textwidth]{figures/kcont_exp}

        \caption{Turbulence kinetic energy at $x/D=1$ from experiments
            \cite{Bachant2015-RVAT-Re-dep-data}.}

        \label{fig:kcont-exp}
    \end{subfigure}

    \begin{subfigure}[b]{\textwidth}
        \centering

        \includegraphics[width=0.95\textwidth]{figures/kcont_kOmegaSST}

        \caption{Turbulence kinetic energy at $x/D=1$ computed by the 3-D SST
            model.}

        \label{fig:kcont-SST}
    \end{subfigure}

    \begin{subfigure}[b]{\textwidth}
        \centering

        \includegraphics[width=0.95\textwidth]{figures/kcont_SpalartAllmaras}

        \caption{Turbulence kinetic energy at $x/D=1$ computed by the 3-D SA
            model.}

        \label{fig:kcont-SA}
    \end{subfigure}

    \caption{Turbulence kinetic energy from experiments and 3-D CFD cases. Solid
        black lines indicate turbine frontal area.}

    \label{fig:kcont}
\end{figure}
